Work Fragmentation in Developer Interaction Data

### 2016-02-11 paper_2.tex
Minor changes

\author{Luis C. Cruz$^{\S}$, Heider Sanchez$^{\ddagger}$, Romain Robbes$^{\ddagger}$, Victor M. Gonzalez$^{\S}$}

@@

In this section we analyze whether or not the interruption duration is a factor in the relationship between interruptions and developer productivity. Under the hypothesis that prolonged interruptions require more time to recover, we have built three groups of sessions based on the proportion of long interruptions. As we described previously about the kind of interruptions we consider, a prolonged interruption are those whose duration is $\geq$12 minutes, and could be due to an extended interruption, a coffee break or meeting.

The proportion of long interruptions is calculated as the sum of interruptions longer than 11 minutes, divided by the total of interruptions in that session. Then, we obtain the quantiles of the distribution of this proportion and use them to create 3 groups described like the following:

\begin{itemize}
\item \textit{low}: the first group consists of sessions where the proportion of prolonged interruptions is $<$0.30, which includes sessions with proportion equal to zero, that is sessions with only short interruptions. These sessions constitute 47.7\% in Mylyn and 20.8\% in UDC, from the total of sessions in both datasets.
\item \textit{medium}: the second group consists of sessions with a proportion between 0.30 and 0.50. These sessions constitute 31.8\% in Mylyn and 18.9\% in UDC.
\item \textit{high}: the sessions in this group have a proportion $>$0.50, which are the 20.5\% in Mylyn and 60.1\% in UDC.
\end{itemize}

Following the conclusions on RQ1, the number of interruptions may affect the results if we ignore that variable. So, we split every group in accordance to the number of interruptions; this time, instead of taking the quantiles of the distribution we took the terciles. Also, we separated the sessions with one interruption into new group. Thus, for the three metrics, we created the groups low, medium and high, and every group was split in other four groups according to the terciles of the distribution of the number on interruptions.

@@

We did so by computing Cohen's $d$ on the quantity of edits before and after the interruption. To obtain a significant effect, we need the presence of activity both before and after. Not all the interruptions meet this criteria however: some are located close to the start or the end of a session, or too close to another interruption.  In total, 53\% of the interruptions had 30 minutes before and after the interruption and were selected for the analysis.  The remaining 47\% of the interruptions can not be used on this analysis due to the lack of time around them. %We used the Algorithm \ref{alg:local_effect} for the classification, and the 
Table \ref{tbl:local_effect} shows the applied thresholds and the results, accompanied with a typical example of an interruption in each category. This local analysis shows that there are indeed three well-defined groups of interruptions, with the two largest of them having clear effects on the activity in the session.

>>>>

\author{Luis C. Cruz $^{\S}$, Heider Sanchez$^{\ddagger}$, Romain Robbes$^{\ddagger}$, Victor M. Gonzalez$^{\S}$}

@@

In this section we analyze whether or not the interruption duration is a factor in the relationship between interruptions and developer productivity. Under the hypothesis that prolonged interruptions require more time to recover, we have built three groups of sessions based on the proportion of long interruptions. As we described previously we consider prolonged interruption are those whose duration is $\geq$12 minutes, according to previous work \cite{GM04, KaptelininN07}. Prolonged interruptions could be due to an extended interruption, such as a coffee break or a meeting.

The proportion of long interruptions is calculated as the sum of interruptions longer than 11 minutes, divided by the total of interruptions in that session. Then, we obtain the quantiles of the distribution of this proportion and use them to create 3 groups described in the following:

\begin{itemize}
\item \textit{low}: the first group consists of sessions where the proportion of prolonged interruptions is $<$0.30; this includes sessions for which the proportion of long interruption is zero, that is, sessions with only short interruptions. These sessions constitute 47.7\% in Mylyn and 20.8\% in UDC, from the total of sessions in both datasets.
\item \textit{medium}: the second group consists of sessions with a higher proportion of long interruptions, between 0.30 and 0.50. These sessions constitute 31.8\% in Mylyn and 18.9\% in UDC.
\item \textit{high}: finally, more than half the sessions in the last group are pronlonger (proportion $>$0.50). This represents 20.5\% of the sessions in Mylyn and 60.1\% in UDC.
\end{itemize}

%Following the conclusions on RQ1, the number of interruptions may affect the results if we ignore that variable. So, we split every group in accordance to the number of interruptions; this time, instead of taking the quantiles of the distribution we took the terciles. Also, we separated the sessions with one interruption into new group. Thus, for the three metrics, we created the groups low, medium and high, and every group was split in other four groups according to the terciles of the distribution of the number on interruptions.

Following the conclusions on RQ1, the number of interruptions may affect the results if we ignore that variable. So, we split every group in accordance to the number of interruptions; this time, instead of taking the quantiles of the distribution we took the terciles \RR{Why?}. Thus, for the three metrics, we created the groups low, medium and high, and every group was split three additional groups according to the terciles of the distribution of the number on interruptions.

@@

We did so by computing Cohen's $d$ on the quantity of edits before and after the interruption. To obtain a significant effect, we need the presence of activity both before and after the interruption. Not all the interruptions meet this criteria however: some are located close to the start or the end of a session, or too close to another interruption.  In total, 53\% of the interruptions had 30 minutes before and after the interruption and were selected for the analysis.  The remaining 47\% of the interruptions can not be used on this analysis due to the lack of time around them. %We used the Algorithm \ref{alg:local_effect} for the classification, and the 
Table \ref{tbl:local_effect} shows the applied thresholds and the results, accompanied with a typical example of an interruption in each category. This local analysis shows that there are indeed three well-defined groups of interruptions, with the two largest of them having clear effects on the activity in the session.
